Software Architectures to Integrate Workflow Engines in Science Gateways

### 2016-04-27 paper.tex
Added a paragraph in discussion (@merous comment).

Finally, the particular technical or historical context of a science
gateway project may obviously influence the choice of an architecture
to integrate workflow engines. For instance, some workflow engines may
be already available as web services, which would tend to favor
service invocation, and other science gateways may have strongly
tested task and data control features (interactions \texttt{b} and
\texttt{c}), which would favor sub-tasking. Similarly, adding a new
type of engine may facilitate integration of a new infrastructure when
interactions \texttt{b} and \texttt{c$_2$} are already available. The
migration cost between architectures has been ignored as well.

>>>>

The particular technical or historical context of a science gateway
project may obviously influence the choice of an architecture to
integrate workflow engines. For instance, some workflow engines may be
already available as web services, which would tend to favor service
invocation, and other science gateways may have strongly tested task
and data control features (interactions \texttt{b} and \texttt{c}),
which would favor sub-tasking. Similarly, adding a new type of engine
may facilitate integration of a new infrastructure when interactions
\texttt{b} and \texttt{c$_2$} are already available. The migration
cost between architectures has been ignored as well.

Finally, workflow engines are only one of the many aspects involved in
the design of a science gateway. Other properties definitely influence
the design of a software architecture, for instance collaborative
features, data visualization, search, authentication, accounting and
so on.
